Contextual Combinatorial Cascading Bandits

### 2016-02-04 contextual combinatorial cascading bandits.tex
modify

We evaluated $C^3$-UCB in three experiments and compared our algorithm to {\it CombCascade}, the most related one to ours. And we set the position discounts $\gamma_k$ to be $\gamma^{k-1}$ for some $\gamma$.

>>>>

We evaluated our algorithm, $C^3$-UCB, in a synthetic setting and two real applications. The results are compared with {\it CombCascade}, the most related study to ours, and demonstrate the advantage to involve contextual information and position discounts. In experiments, we set the position discounts $\gamma_k$ to be $\gamma^{k-1}$ for some $\gamma$.
